A Fast Unified Model for Parsing and Sentence Understanding

### 2016-03-18 writing/hard_stack_paper/paper.tex
Trim section 3.2

The core SPINN model implements a sequential shift-reduce parser which operates over sentences. It is designed to produce a vector representation of the sentence as output, as opposed to a tree as in standard shift-reduce parsing. This relies on two key modifications to the shift-reduce algorithm. First, the parser's intermediate representations, including those of partial tree structures on the stack, are fixed-length vectors. In addition, the \reduce~operation combines two such vectors from the stack into another vector using a neural network function.

\paragraph{The composition function}
When a \reduce~operation is performed, vector representations of two tree nodes are popped off of the head of the stack and fed into a {\it composition function}, which is a neural network function that produces a representation for a new tree node that is the parent of the two popped nodes. This new node is then pushed on to the stack.

>>>>

The core SPINN model implements a sequential shift-reduce parser which operates over sentences. It is designed to produce a vector representation of the sentence as output, as opposed to a tree as in standard shift-reduce parsing. SPINN is an extension of the shift-reduce model whose intermediate representations, including those of partial tree structures on the stack, are fixed-length vectors. Its \reduce~operation combines two vector representations from the stack into another vector using a neural network function.

\paragraph{The composition function}
When a \reduce~operation is performed, the vector representations of two tree nodes are popped off of the head of the stack and fed into a {\it composition function}, which is a neural network function that produces a representation for a new tree node that is the parent of the two popped nodes. This new node is then pushed on to the stack.
